The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add weighted value extension

>>>>

::: {.fragment}
 - Endow the game with a weight system
   - The platform has weight $\lambda$
   - The firms have weight $1$
 - Weights can thoughts of as innate bargaining power [@shapley1953additive; @hart1973values]
:::

::: {#prp-weighted .fragment}
## Weighted values
Let $f(t)$ be continuous on $[0, 1]$. Then
$$
   \varphi_P^\infty(f, \lambda) = \int_0^1 \underbrace{\lambda t^{\lambda - 1}}_{g(t)} f(t) \mathrm{d}t
$$
:::

::: {.notes}
 - The limit of weighted values is *new*
 - Corollaries give credence to the bargaining power interpretation
 - Probabilistic interpretation (weighting permutations)
:::
